### 2020-04-07 draft.tex
fixed proofs

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
where the family of sets $E_b$ depends on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

\[
[image]
\]

$B$ is the set of rows and $E_b$ is the set of boxes in row $b$ (possibly empty,
for generalities sake). We can see the polynomial functor \eqref{eqn.poly}
as sending a set $X$ to the set of ways to label a row of the correponding Young
diagram with elements of $X$.

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a pair of functions%
\footnote{We use dependent type syntax, in particular Idris$^?$.}
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
noting that $f$ acts covariantly on \dis{columns, right?} and $f^\sharp$ acts contravariantly on
boxes in each row. We refer to these special spans as \dis{can we say \emph{bivariant?}} \emph{contravariant} morphisms of bundles.
In terms of bundles, this is a diagram of the following sort:
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"'] \arrow[r, leftarrow, "f_{\sharp}"] & \bullet \arrow[d] \arrow[r]
    \arrow[dr, phantom, "\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
    B \arrow[r, equals] & B \arrow[r, "f"'] & B'
  \end{tikzcd}
\]

@@

This begs the question: what, then, are we to make of the more obvious,
\emph{\dis{univariant?}} morphisms of bundles
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
for which $f$ is covariant in the rows and $f_\sharp$ is again covariant
in each row.
%which, in terms of Young diagrams, are covariant on both the rows and the boxes
%in each row?

It turns out that these covariant maps of bundles correspond to natural
transformations between the appropriate sums of \emph{contravariant}
representables:
$$D(X) := \sum_{b \in B} E_b^X$$
In terms of Young diagrams, such a functor takes a set $X$ to the set of ways to
place the elements of $X$ in the boxes of a row.

Polynomial functors as in \eqref{eqn.poly} get their name from the case in which $B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to \Nb$, which takes the cardinality of each column $E_b$. Letting $B_n := (\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of columns with $n$ elements,
we find that the for any set $X$, the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
resembles a Dirichlet series in the cardinality of $X$. Accordingly, we call such
sums of contravariant representables \emph{Dirichlet functors}. Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree? Maybe there's a better place to put this?}

We will show in this paper that Dirichlet functors are, quite robustly, the
contravariant analogue of polynomial functors. In particular, the many equivalent ways to
say that a functor is polynomial have contravariant analogues.
\begin{thm}[cite]\label{thm:polynomial.set.characterization}
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent.
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is the sum of covariant representables.
  \item There is a bundle $\pi : E \to B$ together with a natural isomorphism
    $$P(X) \cong \sum_{b \in B} X^{E_b}.$$
    Or, equivalently, a natural isomorphism of $P$ with the composite
    $$\Set \xto{\dis{\Delta_{!_E}}} \Set_{/E} \xto{\dis{\Pi_\pi}} \Set_{/B} \xto{\dis{\Sigma_{!_B}}} \Set.$$
  \item $P$ is accessible and preserves connected limits.
  \end{enumerate}
\end{thm}

Analogously, we will prove the following theorem.
\begin{thm}\label{thm:dirichlet.set.characterization}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{\Sigma_{!_B}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more manageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set \dis{also the terminal twisted arrow; any relation to GHK?}. As a corollary, Dirichlet functors form a topos.

@@

Now, object-wise, a Dirichlet functor and a polynomial functor are determined by
the same data --- a bundle $\pi : E \to B$ of sets. Accordingly, one would
expect for any set $N$ a transformation
$$X^N \mapsto N^X$$
turning polynomial functors into Dirichlet functors, and vice versa. But the
natural transformations between each sort of functor induce different morphisms
between the bundles; natural transformations between polynomial functors induce
contravariant bundle morphisms, while natural transformations between Dirichlet
functors induce covariant bundle morphisms. However, if we restrict to those
morphisms of bundles which are \emph{isovariant} on the fibers --- that is, the
pullback diagrams of the form
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
which preserve the number of boxes in each row --- we find that such a morphism
is both a co- and contravariant morphism of bundles. It is well known that such
\emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
transformations between polynomial functors (cite) --- those whose naturality
squares are pullbacks. This is true as well for Dirichlet functors.
\begin{thm}
A natural transformation $D \to D'$ of Dirichlet functors is Cartesian if and
only if the corresponding bundle map
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
is a pullback. As a corollary, we have an equivalence of categories
$$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
between polynomial functors with cartesian natural transfromations and Dirichlet
functors with cartesian natural transfromations.
\end{thm}

This story occupies Section \ref{sec:set.level} of our paper.

Polynomial functors play another very important role: they are \emph{generating
  functors} for flat combinatorial species. That is, we have a (non-canonical)
identification
$$P(X) \cong \sum_{n \in \Nb} C_n \times X^n/n!$$
for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely
(for \emph{finitary} functors $P$, i.e.\ those that commute with filtered colimits).
The generating functors for general combinatorial species --- the \emph{analytic
functors} --- are not in general polynomial due to a loss of information when
quotienting out by the action of the symmetric groups. This can be fixed by
instead taking \emph{homotopy quotients} of these actions.

In other words, we need to move to homotopy types to make sense of the
fractional coefficients that arise in the exponential power series form
$$\sum_{n \in \Nb} a_n \frac{x^n}{n!}.$$
As we will see, moving to homotopy types also allows us to express the negative
exponent in the Dirichlet series form
$$\sum_{n \in \Nb} a_n n^{-s}.$$

In \emph{$\infty$-Operads as Analytic Monads} \cite{GHK:Analytic.Monads},
Gepner, Haugseng, and Kock take this approach and develop the theory of
polynomial functors on homotopy types. In this setting, being analytic is a
property of \dis{some?} polynomial functors, and is equivalent to admitting a cartesian
map to the functor $\type{Sym}$ given by
$$\type{Sym}X := \sum_{n : \Nb} X^n \sslash n!$$
\dis{This is the homotopy quotient?}

Let $\Ha$ be the $\infty$-category of homotopy types. GHK prove $\infty$-categorical analogues of the above Theorem
\ref{thm:polynomial.set.characterization}.
\begin{thm}[\cite{GHK:Analytic.Monads}]\label{thm:polynomial.type.characterization}
For any functor $P : \Ha \to \Ha$, the following are equivalent:
  \begin{enumerate}
  \item $P$ is polynomial.
  \item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
    $$P(X) \simeq \sum_{b : B} X^{E_b}.$$
    Or, equivalently, a natural equivalence of $P$ with the composite
    $$\Ha \xto{E^{\ast}} \Ha_{/E} \xto{\pi_!} \Ha_{/B} \xto{B_\ast} \Ha.$$
  \item $P$ is accessible and preserves weakly contractible limits.
  \end{enumerate}
\end{thm}

Note that while this is a strong analogue, it is not a direct generalization of \cref{thm:polynomial.set.characterization}:
though it is true that in 1-categories all connected limits are weakly contractible, this is not true in general.

In Section \ref{sec:type.level}, we will prove analogues of Theorems
\ref{thm:dirichlet.set.characterization} and
\ref{thm:dirichlet.set.equivalence}. \dis{What analogue of \ref{thm:dirichlet.set.equivalence} are we proving?} In particular, we will prove the following.

\begin{thm}\label{thm:dirichlet.type.characterization}
Let $D : \Set\op \to \Set$ \dis{Do you mean $\Ha$ here?} be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet. \dis{In what sense?}
\item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural equivalence of $D$ with the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item $D$ preserves weakly contractible limits.
\end{enumerate}
\end{thm}

In Section \ref{sec:ordinary.dirichlet.functors}, we will introduce the notion
of an \emph{ordinary} Dirichlet functor, a categorification of a Dirichlet
series
$$\sum_{n \in \Nb} a_n n^{-s}.$$
In the last installment of his blog \emph{This Week's Finds} (cite), Baez (joint with
Dolan) presents a functor of groupoids categorifying the Riemann Zeta function.
In later, unpublished work (cite), Baez and Dolan give an analogous
categorification of Hasse-Weil Zeta functions. We will recall some facts about
homotopy cardinality and construct these Zeta functors as ordinary Dirichlet
functors in our setting. We leave the investigation of Euler product formulas
and functional equations on the objective level to future work.

@@

\section{Dirichlet Functors on Sets} \label{sec:set.level}

@@

\begin{prop}
  There is an adjoint quintuple:
  \[
    \begin{tikzcd}
      \Set \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Set^{\down}
    \end{tikzcd}
  \]
  All three functors $\Set \to \Set^{\down}$ are fully faithful.\dis{I had six; why leave one off?}
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple; the outer two are
given by Kan extending, or more concretely:
  \begin{equation}\label{eqn.bangbang}
  X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
  \qquad\text{and}\qquad
  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}
  \end{equation}
\dis{Shouldn't the notation $!^X$ and $!_X$ be switched, so that $X$ is contravariant in $X\to \ast$ and covariant in $0\to X$? It also matches the side of the arrow that $X$ is on in \eqref{eqn.bangbang}.} It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all three functors
going from $\Set \to \Set^{\down}$ are fully faithful.
\end{proof}

@@

\begin{defn}\label{def.extent}
  Consider the functor $!_0 : \down \to \Set\op$ picking out the unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to its precomposition with $!_0$ gives an evaluation functor
  $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
  \dis{I worry about the size of $\Fun(\Set\op,\Set)$.}\jaz{No need to worry,
    you are extending functors with small domains along a functor with small
    domains. Limits in any functor category (regardless of size) are calculated
    pointwise, and we are taking small limits.} 
  This functor admits a right adjoint by right Kan extension along $!_0\op \circ
  \sigma : \downarrow \to \Set\op$; we define the
  \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
  \Set)$ to be this right adjoint. It sends any bundle $\pi$ to
  $$\ext_{\pi} :\equiv \term{ran}_{!_0\op \circ \sigma} \pi.$$
\end{defn}

\begin{prop}
  The functor $\ext$ is fully faithful, giving an equivalence
  $$\Set^{\down} \simeq \Dir$$
  where $\Dir$ is the category of Dirichlet functors and natural transformations.
\end{prop}
\begin{proof}
Since $!_0 : \down \to \Set\op$ is fully faithful, the counit of the
$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
right Kan extension --- is an isomorphism. 
\end{proof}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$ from \cref{def.extent}.
  \item The functor
    $$S \mapsto \sum_{b \in B} E_b^S,$$
    or equivalently the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item \dis{Add this?} The pullback functor sending a set $S$ to 
\[
\begin{tikzcd}
	\ext_\pi(S)\ar[r]\ar[d]\arrow[dr, phantom,
      "\ulcorner" very near start]&
	B\ar[d]\\
	\Set(S,E)\ar[r]&
	\Set(S,B)
\end{tikzcd}
\]
\item The restricted representable functor
  $\Set^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Set}(!_0, S) \to \down \xto{\pi} \Set)$$
  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Set$ over $S$.\dis{Is this Emily's notation for comma category?}\jaz{yes in
    her Elements}
\item The functor
  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{\pi} \Set)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone} 2-functor, adjoining an initial object.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \down \xto{\pi} \Set)$$
is the standard right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ as a conical limit. Noting that $\Hom_{\Set}(!_0, S) = \Hom_{\Set\op}(S,
!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
$\Hom_{\Set}(!_0, S)$ simply adjoins an initial object to (the discrete
category) $S$, we see that (4) is equivalent to (5).

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}}\down \xto{!_0} \Set$, namely:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkRyQBfU9TXfIRTkK1Ok1btOPPtjwEiAZlE0GLNog7deIDHMFEALCvHqp22QIUoATCbWTNAHScBjKBBwIZu-vKHIdjZiDhogxBa++taBpMQhEmEAGtxiMFAA5vBEoABmAE4QALZIAKw0OBBIxD4FxWUVVYjktYUliOUglUg2rfUdjUiKfe1kXU0AbCNIIuNIUzp17XZziAt5bUODa1yUXEA
\begin{tikzcd}
              &              & S                                               &              &               \\
1 \arrow[rru] & 1 \arrow[ru] & \cdots                                          & 1 \arrow[lu] & 1 \arrow[llu] \\
              &              & 0 \arrow[llu] \arrow[lu] \arrow[ru] \arrow[rru] &              &              
\end{tikzcd}
\]
Since, by Lemma \ref{lem:bang.preserves.connected.colimits}, $!_{(-)}$
preserves connected colimits, {\color{red} TODO}.

Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
isomorphic to the set $\sum_{b \in B} E_b^X$.\dis{add pullback?}
\end{proof}

Now we are ready to intrinsically characterize the Dirichlet functors.
\begin{thm}
A functor $D : \Set\op \to \Set$ is Dirichlet if and only if it preserves
connected limits. 
\end{thm}
\begin{proof}
First, we show that Dirichlet functors preserve connected limits. If $D$ is
Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
isomorphic to the composite
$$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
\xto{B_\ast} \Set.$$
As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$
is part of a multivariable adjunction, it also commutes with all limits.
Finally, we note that $B_{\ast}$ commutes with connected limits.

>>>>

\begin{abstract}
  Polynomial functors are sums of covariant representable functors from the
  category of sets to itself. They have a robust theory with many applications
  --- from operads and opetopes to combinatorial species. In this paper, we
  define a contravariant analogue of polynomial functors: Dirichlet functors. We
  develop the basic theory of Dirichlet functors, and relate them to their
  covariant analogues.
\end{abstract}

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
where the family of sets $E_b$ depends on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}.

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a pair of functions%
\footnote{We use dependent type syntax, in particular Idris$^?$.}
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
noting that $f$ acts covariantly on the base and $f^\sharp$ acts contravariantly on
fibers. 
In terms of bundles, this is a diagram of the following sort:
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"'] \arrow[r, leftarrow, "f_{\sharp}"] & \bullet \arrow[d] \arrow[r]
    \arrow[dr, phantom, "\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
    B \arrow[r, equals] & B \arrow[r, "f"'] & B'
  \end{tikzcd}
\]
We refer to these special spans as \emph{contravariant} morphisms of bundles.

@@

This begs the question: what, then, are we to make of the more obvious,
\emph{covariant} morphisms of bundles
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
for which $f_\sharp$ is covariant
in each fibers.

It turns out that these covariant maps of bundles correspond to natural
transformations between the appropriate sums of \emph{contravariant}
representables:
$$D(S) := \sum_{b \in B} E_b^S$$

Polynomial functors as in \eqref{eqn.poly} get their name from the case in which
$B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to
\Nb$, which takes the cardinality of each fiber $E_b$. Letting $B_n :=
(\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of elements whose fibers have $n$ elements,
we find that the for any set $X$, the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(S)| = \sum_{n \in \Nb} |B_n|n^{|S|}$$
resembles a Dirichlet series in the cardinality of $S$ -- without the usual
negative sign.\footnote{Future work of the first author will recover the
  negative sign by generalizing the theory of Dirichlet functors to homotopy
  types.} Accordingly, we call such
sums of contravariant representables \emph{Dirichlet functors}.

We will show in this paper that Dirichlet functors are, quite robustly, the
contravariant analogue of polynomial functors. In particular, the many equivalent ways to
say that a functor is polynomial have contravariant analogues.
\begin{thm}[cite]\label{thm:polynomial.set.characterization}
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent.
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is the sum of covariant representables.
  \item There is a bundle $\pi : E \to B$ together with a natural isomorphism
    $$P(X) \cong \sum_{b \in B} X^{E_b}.$$
    Or, equivalently, a natural isomorphism of $P$ with the composite
    $$\Set \xto{{\Delta_{!_E}}} \Set_{/E} \xto{{\Pi_\pi}} \Set_{/B} \xto{{\Sigma_{!_B}}} \Set.$$
  \item $P$ is accessible and preserves connected limits.
  \end{enumerate}
\end{thm}

Analogously, we will prove the following theorem.
\begin{thm}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{\Sigma_{!_B}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more manageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set. As a corollary, Dirichlet functors form a topos.

@@

Now, object-wise, a Dirichlet functor and a polynomial functor are determined by
the same data --- a bundle $\pi : E \to B$ of sets. Accordingly, one would
expect for any set $N$ a transformation
$$X^N \mapsto N^X$$
turning polynomial functors into Dirichlet functors, and vice versa. But the
natural transformations between each sort of functor induce different morphisms
between the bundles; natural transformations between polynomial functors induce
contravariant bundle morphisms, while natural transformations between Dirichlet
functors induce covariant bundle morphisms. However, if we restrict to those
morphisms of bundles which are \emph{isovariant} on the fibers --- that is, the
pullback diagrams of the form
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
which preserve the number of elements in each fiber --- we find that such a morphism
is both a co- and contravariant morphism of bundles. It is well known that such
\emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
transformations between polynomial functors \jaz{ (cite) } --- those whose naturality
squares are pullbacks. This is true as well for Dirichlet functors.
\begin{thm}
A natural transformation $D \to D'$ of Dirichlet functors is Cartesian if and
only if the corresponding bundle map
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
is a pullback. As a corollary, we have an equivalence of categories
$$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
between polynomial functors with cartesian natural transfromations and Dirichlet
functors with cartesian natural transfromations.
\end{thm}

@@

\section{Dirichlet Functors} \label{sec:set.level}

@@

\begin{prop}\label{prop:adjoint.sextuple}
  There is an adjoint sextuple:
  \[
    \begin{tikzcd}
      \Set \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10,
      "!_{(-)}"] \arrow[r, leftarrow, shift left = 15, "\term{ZC}"]& \Set^{\down}
    \end{tikzcd}
  \]
  All three functors $\Set \to \Set^{\down}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple; the outer two are
given by Kan extending, or more concretely:
  \begin{equation}\label{eqn.bangbang}
  X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
  \qquad\text{and}\qquad
  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}
  \end{equation}
 It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all three functors
going from $\Set \to \Set^{\down}$ are fully faithful.

The existence of the final adjoint can be deduced from the fact that $!^{(-)}$ preserves all
limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(B)$ of $B$ for
which the following square is a pullback
\[
  \begin{tikzcd}[column sep=large]
0 \arrow[r] \arrow[d] \arrow[dr, phantom,
"\ulcorner" very near start] & E \arrow[d, "\pi"] \\
\term{ZC}(B) \arrow[r, hookrightarrow]                                       & B
\end{tikzcd}
\]
\end{proof}

@@

\begin{defn}\label{def.extent}
  Consider the functor $!_0\op \circ \sigma : \down \to \Set\op$ picking out the
  unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to
  its precomposition with $!_0\op \sigma$ gives an evaluation functor
  $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
  This functor admits a right adjoint by right Kan extension along $!_0\op \circ
  \sigma : \downarrow \to \Set\op$; we define the
  \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
  \Set)$ to be this right adjoint. It sends any bundle $\pi$ to
  $$\ext_{\pi} :\equiv \term{ran}_{!_0\op \circ \sigma} \pi.$$
\end{defn}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$ from \cref{def.extent}.
  \item The functor
    $$S \mapsto \sum_{b \in B} E_b^S,$$
    or equivalently the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item The pullback in $\Fun(\Set\op, \Set)$:  
\[
\begin{tikzcd}
	\ext_\pi \ar[r]\ar[d]\arrow[dr, phantom,
      "\ulcorner" very near start]&
	B\ar[d]\\
	\Set(-,E)\ar[r]&
	\Set(-,B)
\end{tikzcd}
\]
\item The restricted representable functor
  $\Set^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set)$$
  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Set$ over $S$.
\item The functor
  $$S \mapsto \lim(( S^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
  (\ast^{\triangleleft})\op \xto{\sigma\op} \down
  \xto{\pi} \Set)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone} 2-functor, adjoining an initial object.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
S)\op$ over $\down$, which we may see by noting that $(-)\op : {\infty}\Cat \to {\infty}\Cat^{\term{co}}$ is a cosmological equivalence and therefore preserves
comma squares. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
This gives us the equivalence between (1) and (5).

Now, the comma category $\Hom_{\Set}(!_0, S)$ simply adjoins an initial object
to (the discrete category) $S$. Therefore, we find that (5) and (6) are equivalent.
